\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathpazo}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage[
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue
]{hyperref}
\usepackage{fontawesome5}
\usepackage{enumitem}
\setlist[itemize]{
  label={},        % remove bullets
  leftmargin=1.5em,
  topsep=1pt,
  itemsep=3pt,
  parsep=0pt,
  partopsep=0pt
}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{1ex}{0.5ex}
\titleformat*{\section}{\normalfont\scshape\large}

\begin{document}

\begin{center}
  {\LARGE\bfseries Curriculum Vitae for Jonas Hübotter}\\[4pt]
  {\itshape PhD Student in Computer Science, ETH Zürich}\\[8pt]
  %------------------------------------------------------------
  % \faEnvelope\ \href{mailto:jonas.huebotter@gmail.com}{jonas.huebotter@gmail.com}
  % \quad
  \faGithub\ \href{https://github.com/jonhue}{GitHub}
  \quad
  % \faLinkedin\ \href{https://linkedin.com/in/jonhue}{Linkedin}
  % \quad
  \faGraduationCap\ \href{https://scholar.google.com/citations?user=pxi_RkwAAAAJ}{Publications}
  %------------------------------------------------------------
\end{center}

%-----------EDUCATION-----------------
\section*{Education}
\begin{itemize}[leftmargin=1.5em]
  \item \textbf{Ph.D.\ in Computer Science}, ETH Zürich, since 2023.\ Advisor: Prof.\ Andreas Krause.

  \item \textbf{M.Sc.\ in Computer Science}, ETH Zürich, 2023. \begin{itemize}
    \item Theoretical Computer Science (major) and Machine Learning (minor).
    \item \emph{ETH Medal for best thesis (awarded to top 2.5\% of all ETH graduates).}
  \end{itemize}

  \item \textbf{B.Sc.\ in Computer Science}, Technische Universität München, 2021. \begin{itemize}
    \item Computer Science (major) and Mathematics (minor).
    \item \emph{Passed with distinction.}
  \end{itemize}
\end{itemize}

%-----------POSITIONS HELD-----------------
\section*{Positions (Selected)}
\begin{itemize}[leftmargin=1.5em]
  \item \textbf{Quantitative Researcher (Intern)}, Citadel Securities, London (Jul.'22-Sep.'22) \begin{itemize}
    \item Worked on time-series prediction with Guillaume Basse and Sören Künzel.
    \item \emph{Received a full-time return offer.}
  \end{itemize}
  \item \textbf{Machine Learning Engineer (Part-time)}, Uncountable, Munich (Apr.'20-Jul.'21) \begin{itemize}
    \item Worked on constrained Bayesian optimization and outlier detection for R\&D.
  \end{itemize}
\end{itemize}

%-----------TEACHING-----------------
\section*{Teaching}
\begin{itemize}[leftmargin=1.5em]
  \item {Probabilistic Artificial Intelligence}, ETH Zürich \begin{itemize}
    \item \textsc{Teaching Assistant:} 2022-2025
    \item \emph{\href{https://arxiv.org/pdf/2502.05244}{Lecture notes} written with Andreas Krause.}
  \end{itemize}
  \item {Introduction to Machine Learning (TA)}, ETH Zürich, 2024-2025
  \item {Advanced Graph Algorithms and Optimization (TA)}, ETH Zürich, 2023
  \item {Algorithms and Probability (TA)}, ETH Zürich, 2022
  \item {Theory of Computation (TA)}, Technische Universität München, 2021
  \item {Discrete Probability Theory (TA)}, Technische Universität München, 2021
  \item {Functional Programming and Verification (TA)}, Technische Universität München,~2021
\end{itemize}

%-----------PROFESSIONAL SERVICE-----------------
\section*{Professional Service}
\begin{itemize}[leftmargin=1.5em]
  \item \textsc{Reviewer:} NeurIPS 2024 (top), 2025; ICLR 2025.
\end{itemize}

%-----------ACADEMIC HONORS AND RECOGNITIONS-----------------
\section*{Honors and Awards}
\begin{itemize}[leftmargin=1.5em]
  \item \emph{Swiss AI Grant} for 50k GH200 GPU hours ($\approx\!\$150\mathrm{k}$ value), 2025
  \item \emph{Best Paper Award} at FITML@NeurIPS 2024
  \item \emph{ETH Medal}, 2024
  \item \emph{Graduate Scholarship}, German Academic Scholarship Foundation, 2021
  \item \emph{Undergraduate Scholarship}, German Academic Scholarship Foundation, 2019
\end{itemize}

\end{document}
